# modern approach (temp)

```{r}
knitr::opts_chunk$set(error=TRUE)

```

```{r message=FALSE}
# pkg
library(tidyverse)
library(janitor)
library(gt)
library(broom)

```


```{r message=FALSE}
# read data
playbill_dat <- read_csv('data/modernapproach/playbill.csv')

# take a look at the raw data
head(playbill_dat)

```


```{r}
# visualise relationship prior to plotting
playbil_vis <-
    playbill_dat %>%
        ggplot(aes(x = LastWeek, y = CurrentWeek)) +
        geom_point() +
        theme_minimal() + 
        labs(
            title = "Playbill weekly box office earnings",
            x = "Previous week",
            y = "Current week",
            caption = 'playbill.csv'
        )
```

We wish to test, first, if it plausible that $B_1 = 1$, under the assumption that each value of the Current week's box office earnings $y$ can be thought of in terms of an average boxoffice earnings and the previous week's earnings, allowing for some error per observation, so that $y = \beta_0 + \beta_1 x + \varepsilon$.

A relevant example is the runtime example from the chapter (p.19). 


```{r}
# set results to check

int <- 149.74770
slope <- 0.25924

prod_dat <- read_delim('data/modernapproach/production.txt',
    col_names = c('Case', 'RunTime', 'RunSize'), col_types = 'd', skip = 1)  


head(prod_dat)

```


```{r}

prod_mod <- lm(RunTime ~ RunSize, data = prod_dat)

# check I got the same as sheapther
round(prod_mod$coef, 5) == c(int, slope)


```



```{r}

# back to the playbill data
playbill_mod <- lm(CurrentWeek ~ LastWeek, data = playbill_dat)

summary(playbill_mod)

playbill_mod$coef

tidy(playbill_mod)
augment(playbill_mod)
glance(playbill_mod)

round(confint(playbill_mod),4)



```
```{r}



```
