---
title: "twitter"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

I want to find some tweets where we discuss my visit to Stockholm. So, I wish to search my twitter feed for the character string `"Stockholm"`. 

I haven't tried twitter scraping before, this seems as good as anywhere to start. 

I searched for the terms "tidyverse", "twitter", "scrape" and found a [tutorial](https://idc9.github.io/stor390/notes/API/twitter/rtweet.html) about the `rtweet` package. Seems to be mentioned often enough and recently enough for it to be a good candidate. 

Alrighty, let's begin.

```{r Load packages}
library(tidyverse)
library(rtweet)
library(rvest)

```

I'm not entirely sure what all this business of access tokens is for. I wonder if I need to set them just to scrape the public feed?

```{r try timeline}
# timeline <- get_timeline("cantabile") # This did not work.

```

## Getting access to twitter

For this part, I was directed to [these instructions](http://rtweet.info/articles/auth.html). I was curious to find out if I was required to set this up just to access my feed; i.e., not write to it. I found I did need to set this up. 

```{r create token}
# App
# appname <- "cantabilertweet"

# api key stored in object 'key'
# secret stored in object secret

# twitter_token <- create_token(app = appname,
#                               consumer_key = key,
#                               consumer_secret = secret)

```

## Scraping twitter

Okay, let's try this again.

```{r trying again}
cantabile_timeline <- get_timeline("cantabile", n = 3200)

# Take a look.
cantabile_timeline %>% str(max.level = 1)

```

## Find the string `"Stockholm"`.

Let's make sure I understand how strings work. I may need to go to the `stringr` cheatsheet.

```{r Testing out strings}

stockholm_string <- "Stockholm is a very fine place."

# This doesn't work.
"Stockholm" %in% stockholm_string

# What about this?
"Stockholm" %in% str_split(stockholm_string, pattern = " ")

# Curious.
str_split(stockholm_string, pattern = " ")

# Is it because of its class?
str_split(stockholm_string, pattern = " ") %>% class()

# Make it a character vector.
stockholm_vector <- stockholm_string %>% str_split(pattern = " ")

# Class of vector
stockholm_vector %>% class()

# Take a look.
stockholm_vector

# Try converting to character string.
"Stockholm" %in% stockholm_vector[[1]]
```

## Extract my tweets that mention Stockholm

```{r Filter to my tweets}
my_tweets <- cantabile_timeline %>% 
  filter(is_quote == FALSE, # Remove quotes.
         is_retweet == FALSE # Remove retweets.
         ) %>% 
  mutate( # Tokenise text.
    twit_vector = map(text, str_split, pattern = "\\s"),
    twit_vector = tolower(twit_vector), # Convert words to lower case.
    stockholm = map_lgl(twit_vector,
                        .f = function(a_tweet) {
                          "the" %in% a_tweet
                        }) # See if Stockholm is there.
         ) 

# Take a look.
my_tweets$twit_vector[[1]]


# Testing that Stockholm produces what I want.
my_tweets$stockholm %>% table()

# %>% 
#   filter(
#     Stockholm == TRUE
#   )


```


## Extract responses to those tweets

