---
title: "mash it up"
author: "Charles T. Gray"
date: "6 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load packages}

library(tidyverse)

devtools::install_github("softloud/varameta") # While in development.
library(varameta)

```


## Okay, so for the meta-analysis

I want to run a simulation and replicate it many times.

Let's do this for one set of parameters. 

> How to do this for different distributions? This is it's own whole thing. I can't let this derail the whole meta-analysis simulation. 

The author does this algorithmically, I should follow along with the steps. 

1. Simulate some data and output some summary. 
2. Create a function that simulates the data.
3. Uses replicate to repeat the process many times. 

## First simulate the data

We want to simulate two arms. 

I need to get the algebra right to get the code right.

Let's start with assuming that for study $k$ from $K$ studies, we have observed sample medians $\hat\nu_1$ and $\hat\nu_2$, so we can calculate the log-ratio of the sample medians.   



```{r simulation}

# Choose a sample size.
n <- 30

# Choose a distribution.
distribution <- "cauchy"
parameters <- list(location = -3, scale = 1)

# What does the probability density of this distribution look like?
tibble(x = c(-5, 5)) %>% 
  ggplot(aes(x = x)) + 
  stat_function(fun = dcauchy, args = parameters)

# Number of trials per simulation.
trials <- 10

```

First we start with a random vector.

```{r random vector}
rcauchy(n = n, location = parameters[[1]], scale = parameters[[2]])
```

Now, we're going to want two random samples per trial.

What the location and the scale are what *matter*. We need to generate them.

We're assuming that $E(y_k) = \mu + \theta_k + \varepsilon_k$ with $\theta_k \sim (0, \tau)$ and $\varepsilon_k \sim N(0, \sigma^2)$. 



## Wrap it in a function

## Then use replicate or rerun to repeat the process for simulations

