---
title: "purrr simulations blogpost"
author: "Charles T. Gray"
date: "6 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}

set.seed(16)


```


## The `replicate` function

I'm pretty sure `purrr:rerun` is the same as replicate but with `simplify = FALSE`. 

Anyway, interestingly, `replicate` is from the *apply* family of functions. 

So, `replicate` takes three arguments:

argument | description
`n` | number of replications to perform
`expr` | a function
`simplify` | output as array or list

This seems super handy for what I do. 

The author considers the normal distributio and sampling from it some number of times. 

Let's see how much I can figure out on my own. 

```{r}
# First I'll consider the rnorm function.
rnorm(n = 6, mean = 3, sd = 2)

# Then, how to do this 5 times?

replicate(
  n = 5,
  rnorm(n = 6, mean = 3, sd = 2),
  simplify = FALSE
)


```

Okay, so good so far. 

Note, if we use `simplify = TRUE` we get a matrix of results.

```{r}
replicate(
  n = 5,
  rnorm(n = 6, mean = 3, sd = 2),
  simplify = TRUE
)
```

## Wrap it up like a present in a function

From the previous blogpost on writing simulations 


```{r}
twogroup_fun = function(nrep = 10, b0 = 5, b1 = -2, sigma = 2) {
     ngroup = 2
     group = rep( c("group1", "group2"), each = nrep)
     eps = rnorm(ngroup*nrep, 0, sigma)
     growth = b0 + b1*(group == "group2") + eps
     growthfit = lm(growth ~ group)
     growthfit
}

# Take it for a spin.
twogroup_fun()

```

## Using `purrr::map` for looping through lists

