---
title: "purrr simulations"
author: "Charles T. Gray"
date: "2 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


```

```{r load packages, message=FALSE}
library(tidyverse)

```


A starting place is this [blogpost](https://aosmith.rbind.io/2018/06/05/a-closer-look-at-replicate-and-purrr/).

But the author also points to earlier posts. I wonder if I should start there?

Might as well. It's not like I'm busy ;) 

## A linear model

Following along with [this post](https://aosmith.rbind.io/2018/01/09/simulate-simulate-part1/).

I quite like the way the author wrote up this linear model using an indicator variable. 

$$
y_t = \beta_0 + \beta_1 \cdot I_{\text{group}_t = \text{group}} + \varepsilon_t
$$
but I think still prefer the more generalisable 
$$
y_i = \beta_0 + \beta_1 x_i + \varepsilon_i 
$$

where  

- $y_i \in \mathbb R$ is the $i^\text{th}$ observation
- this model has two groups, so
$$
x_i = 
\begin{cases}
0 & \text{if } y_i \in  \text{group } 1\\
1 & \text{if } y_i \in  \text{group } 2
\end{cases}
$$

- $\beta_0$ represents the mean response for the first group
- $\beta_1$ represents the *difference* between the two groups
- the observations are assumed to be i.i.d. such that $y_i \sim N(0, \sigma^2)$ as a consequence of $\epsilon_i \sim N(0, \sigma^2)$

I like thinking about it this way because I can see the generalisability to multiple dependent variables 

```{r set seed}
set.seed(16) # Ensures I will get the same results as the tutorial.

```

Curiously, I just learnt that we're not using true random number generator, but a *pseudo* random number generator that is *fully* algorithmic. This is deliberate for reproducibility. 

We define the parameters of the mdoel. 

```{r}
ngroup <- 2
nrep <- 10
b0 <- 5
b1 <- -2
sd <- 2


```

Here the author does it one vector at a time, for educational purposes, but I think we can handle tidying this. 

```{r}
sim_data_lm <- tibble(# Assign to two groups - in this case equally.
  group = rep(c("group1", "group2"), each = nrep)) %>%
  mutate(
    # Calculate the random error.
    epsilon = rnorm(ngroup * nrep, 0, sd),
    # Now simulate the observation using the model.
    growth = b0 + b1 * (group == "group2") + epsilon # Nice trick!
  )

# Take a look.
sim_data_lm %>% head() %>% knitr::kable()

```

Okay, now we can fit the model.

```{r}
lm(growth ~ group, data = sim_data_lm) %>% summary()

```


### Make a function for the simulaton

Okay this also looks different from how I've been constructing simulations. Wrap each simulation as a function and vary the simulation parameters. Interesting! 

```{r}
twogroup_fun <- function(nrep = 10, b0 = 5, b1 = -2, sigma = 2) {
  ngroup <- 2
  sim_data <- tibble(# Assign to two groups - in this case equally.
  group = rep(c("group1", "group2"), each = nrep)) %>%
  mutate(
    # Calculate the random error.
    epsilon = rnorm(ngroup * nrep, 0, sd),
    # Now simulate the observation using the model.
    growth = b0 + b1 * (group == "group2") + epsilon # Nice trick!
  )
  # Return a summary of the model.
  lm(growth ~ group, data = sim_data) %>% summary()
}

```

### Repeat the simulation many times using `purrr`

Wow! This is handy! 

The `purrr::rerun` function is apparently analogous to `replicate` with `simplify = FALSE` but I've never used that one, so I'll promptly discard it! 

```{r}
sims <- rerun(1000, twogroup_fun())


```

### Let's tidy up a bit with `broom`

The `broom::tidy` function gives us the coefficients of the 

```{r}
# Extract 

sims %>%
     map_df(broom::tidy) %>% head() %>% knitr::kable()


```

### Using broom functions to produce nice vis

We can examine the distribution of the mean difference between the two groups $\beta_1$. I think is this mean difference, as in each coefficient estimate represents the expected value for that coefficient as estimated by the model from multiple observations. 

```{r}
sims %>%
     map_df(broom::tidy) %>%
     filter(term == "groupgroup2") %>% # To islate beta1
     ggplot( aes(estimate) ) +
          geom_density(fill = "blue", alpha = .5) +
          geom_vline( xintercept = -2)

```

Distribution of estimates of the standard deviation.

*This is a very nice trick.*

```{r}

# sims %>% 
#   map_dbl(~summary(.x)$sigma) %>% 
#   data.frame(sigma = .)


```

Curiously the above doesn't run for me. This is *not* an old post, though. Only from January. 

> Todo here, try to figure out why that code doesn't work sometime (not now).




