---
title: "Awesome Your Data Science "
subtitle: "What analytics can learn from the dev community"
author: "Charles T. Gray (PwC @ NAB)"
date: "Friday 18 January"
output:
  ioslides_presentation
---

 

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

 

##

 

## What my scripts looked like before

 

```
library(numDeriv)
library(plyr)

# S = sqrt(N)*delta (i.e. the non-central t-distributed effect sizes)
# X = covariate vector
# N = Study sample sizes

sim <- F

mr.mle.fixed <- function(S, X, N, method = "nlminb") {
  p <- ncol(X) - 1
  
  K <- length(S)
  
  if (length(N) == 1)
    N <- rep(N, K)
  
  objective <- function(par, S, X, N) {
    b <- par
    
    - sum(log(dt(
      S, df = N - 1, ncp = sqrt(N) * (X %*% b)
    )))
  }

```

 

## What they look like now

 

### Load packages:

```
library(numDeriv)
library(plyr)
```

### Define variables

 

Variable|Definition
-|-
S| $\sqrt N *\delta$ (i.e. the non-central $t$-distributed effect sizes)
X| Covariate vector
N| Study sample sizes


## What they look like now

### Calculate MLE

```
mr.mle.fixed <- function(S, X, N, method = "nlminb") {
  p <- ncol(X) - 1
  
  K <- length(S)
  
  if (length(N) == 1)
    N <- rep(N, K)

  objective <- function(par, S, X, N) {
    b <- par
    
    - sum(log(dt(
      S, df = N - 1, ncp = sqrt(N) * (X %*% b)
    )))
    
  }
  
```

# GitHub-integrated data analytics workflow

## Why did I become obsessed?

- Documention

- Reproducible

- Passes the Tram Test

## In a nutshell

- GitHub repository (think Dropbox)

- **Analysis as a software package**

- Bonus: the `tidy` way of data science

# Analyses as packages

## Packaged analysis workflow

*An example scenario:*

Nick would like to see some exploratory analysis on a new project.

Nick asks Ed to provide him with some modelling.

Ed asks Alex to clean some data first.
Alex cleans, then Ed models, Nick reads the report.

ToDo: Figure out how to do the increment -- thing.

## What could we do?

 

 

## And there's more

 

- Data manipulation becomes efficient and easy

- All files accessible

- Project management

 

## The No Free Lunch Theorem

 

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">ok now listen, the harsh truth is you&#39;re better off writing one thick, messy .Rmd where you keep all your garbage models and weird musings then going off on some precious folder structure and  artfully-named .R files where you can&#39;t find a damned thing ever. <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/oldman?src=hash&amp;ref_src=twsrc%5Etfw">#oldman</a></p>&mdash; Andrew MacDonald (@polesasunder) <a href="https://twitter.com/polesasunder/status/953624238266646529?ref_src=twsrc%5Etfw">January 17, 2018</a></blockquote>

<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

 

 

## Dynamic file types

 

 

```{r echo = FALSE, message = FALSE}

library(shiny)

library(tidyverse)

```

 

 

```{r Shiny app example, echo = FALSE}

true_mean <- 5

 

shinyapp <- shinyApp(

  ui = shinyUI(fluidPage(

    titlePanel("Example interactive simulation, CLT"),

    sidebarLayout(

      sidebarPanel(

 

        sliderInput(inputId = "n",

                    label = "sample size",

                    min = 3,

                    max = 1000,

                    value = 3),

        sliderInput(inputId = "N",

                    label = "trials",

                    min = 3,

                    max = 1000,

                    value = 3),

        sliderInput(inputId = "alpha",

                    label = "alpha",

                    min = 0.0001,

                    max = 0.95,

                    value = 0.05)

      ),

      mainPanel(

        textOutput("ratio"),

        textOutput("prop"),

        plotOutput("hist")# ,

        # dataTableOutput("table")

      )

    )

  )),

  server = shinyServer(function(input, output){

    ci_df <- reactive({

      tibble(

        n = rep(input$n, input$N),

        sample = map(n, rnorm, mean = true_mean, sd = 1),

        mean = map_dbl(sample, mean),

        sd = map_dbl(sample, sd),

        ci_lb = mean - qnorm(1 - input$alpha / 2) * sd / sqrt(n),

        ci_ub = mean + qnorm(1 - input$alpha / 2) * sd / sqrt(n),

        in_ci = true_mean > ci_lb & true_mean < ci_ub

      )

    })

 

    # Ratio.

    output$ratio <- renderText({

      ratio <- round((input$n / input$N), 2)

      paste("The ratio of the sample sizes divided by number of trials:", ratio)

 

    })

 

 

    # Proportion.

    output$prop <- renderText({

      paste(

        "The proportion of confidence intervals that contain the true mean:",

        round(sum(ci_df()$in_ci) / nrow(ci_df()), 2)

      )

    })

 

    output$hist <- renderPlot({

      ci_df() %>%

        ggplot(aes(x = mean)) +

        geom_histogram()

    })

 

    output$table <- renderDataTable({ci_df() %>% select(-sample)})

 

  })

)

 

```

 

 

 

## Resources

 

- `R` packages

- `tidyverse`: the dialect of `R` for data science

 

 

## Thank you for listening

 
