---
title: "Pandas hexes"
author: "Charles T. Gray"
date: "19 April 2018"
output: 
  html_document:
    toc: true
    toc_float: true    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r Packages}
library(tidyverse)

```


## The general idea

I like to draw pandas using crude circles. I often draw them on postits and leave them around friends' workstations. 

So, this could be a great way of me theming my own hexes. Also, I think they're plottable. 

## The theory

Let's suppose we have 

## Plot the pandas

### Shapes required

I want to keep this minimal, so I'll stick with circles. Let's find a circle for:

- the body; 
- the head; 
- the ears and tail; 
- the paws;
- the eyes. 

Plot the text beside the circles, too. 

Also, plot a test panda. 

```{r Circles}
# 5 circles of different sizes
# Can I just do this with geom_point some kind of fill and outline aesthetic? 

# Set distance between the points.
node_distance <- 1

biggest_size <- node_distance / 2

number_of_nodes <- 5 # Can't change without modifying code for size. 

(test <- tibble(
  x = 1,
  y = seq(1, number_of_nodes, by = node_distance),
  size = c(biggest_size, 
           biggest_size / 2, 
           biggest_size / 3,
           biggest_size / 4,
           biggest_size / 8
           ),
  colour = c("black", rep("white", 4)))) 

test %>% 
  ggplot(
    aes(x = x, y = y)
  ) +
  geom_point(aes(size = size,
                 colour = colour),
             shape = 21,
             colour = "black",
             fill = "white"
             ) 


```

### Five pandas, one with a monocle

There is a `data` argument in `geom_point`. I think I should specify the data with each layer.

```{r Plot five pandas}
# Node distance: 1.

body_size <- 10

tibble( # Specify the dimensions of the plot.
  x = c(1, 5),
  y = c(0.5, 1.5)
) %>% 
  ggplot(
    aes(x = x, y = y)
  ) + 
  coord_cartesian(xlim = c(0, 6), ylim = c(0.8, 1.2)) + 
    geom_point( # Body
      data = tibble(x = seq(1, 5, by = 1),
                           y = rep(0.96, 5)),
             size = body_size / 2,
             shape = 21,
             colour = "black",
             fill = "white") +
 geom_point( # Head
   data = tibble(x = seq(1, 5, by = 1),
                         y = rep(1, 5)),
            size = body_size,
            shape = 21,
            colour = "black",
            fill = "white") +
  geom_point( # Feet and hands.
    data = tibble(
      x = 
    )
    
  )
  


```



## Convert to hex
