---
title: "Unpacking the basic example"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

```

## Running through the introductory `greta` example

This introductory example was found on the [front page](https://greta-dev.github.io/greta/) of the `greta` website.

```{r }
library(greta)

x <- iris$Petal.Length
y <- iris$Sepal.Length

int <- normal(0, 5)
coef <- normal(0, 3)
sd <- lognormal(0, 3)

mean <- int + coef * x
distribution(y) <- normal(mean, sd)

m <- model(int, coef, sd)

# Throws error for chains argument, removed chains = 3 & reported issue on github. 
draws <- greta::mcmc(m, n_samples = 1000) 

bayesplot::mcmc_trace(draws)

```

## Now to unpack each element

### First, as always, we start with data

In this case, we're interested in if these data suggest there is an association between `Petal.Length` and `Sepal.Length` in the canonical `iris` dataset.

```{r Get some data}
library(greta)

x <- iris$Petal.Length
y <- iris$Sepal.Length

```

These are two continuous variables.

```{r continuous, message=FALSE, warning=FALSE}

library(tidyverse) # Sorry, Nick. 

iris %>%
  select(Sepal.Length, Petal.Length) %>% 
  gather(key = "variable",
         value = "Length") %>% 
  ggplot(aes(Length)) +
  geom_histogram() +
  facet_wrap(~ variable)

```

This is a simple linear model, one that we used ordinary least squares to solve in undergrad. 

So, for the $i$th observation, we have
$$
Y_i = \beta_0 + \beta_1 X_i + \varepsilon_i
$$
where $\varepsilon_i \sim N(0, \sigma^2)$. Which is to say,
$$
E(Y) = \beta_0 + \beta_1 X.
$$



