---
title: " "
author: "Charles T. Gray"
date: "`r dontpanic::title_date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(dontpanic)

```


<<<<<<< HEAD
# Tasks 
=======




# Tasks
>>>>>>> 5bcc844abb5182a79cc34a887c48d586bc2ce978

- Work through [this](http://db.rstudio.com/dplyr/).

## Uncategorised thoughts

- This [SQL translation](https://cran.r-project.org/web/packages/dbplyr/vignettes/sql-translation.html) thing could be useful.

# Introductory level











# From Glenburn, Wednesday 29 November 2017

- Specific type backend to talk to the relational database management system (RDBMS) of choice.
    - RMySQL connects to MySQL and MariaDB
RPostgreSQL connects to Postgres and Redshift.
    - RSQLite embeds a SQLite database.
    - odbc connects to many commercial databases via the open database connectivity protocol.
    - bigrquery connects to Google’s BigQuery.
    - For this tutorial: **install** RSQLite `install.packages("RSQLite")`
- Next **connect** to the data base using the `DBI` package: `DBI::dbConnect()`.
```{r}
con <- DBI::dbConnect(
  RSQLite::SQLite(), # DB backend .
  path = ":memory:" # Temporary in-memory db.
  )
```
- Then hack some data into the temporary in-memory db. (Only for the tutorial.) 
```{r}
copy_to(
  con, # Specifies object to copy data to.
  nycflights13::flights, # df from an R package
  "flights",
  temporary = FALSE, 
  indexes = list( 
    # Is this akin to group in tidy and key in data.table?
    c("year", "month", "day"), 
    "carrier", 
    "tailnum",
    "dest"
  )
)

# Note that we're hacking an R package df into a RDBMS.
nycflights13::flights %>% 
  head() %>% 
  knitr::kable()
```
- Now we "take a **reference** to it". What does that mean?
```{r}
# Hmm, I don't quite under why this is necessary.
flights_db <- tbl(con, "flights")

# Anyway, now we have a tibble-like object, but the source is different.
flights_db %>% head() %>% knitr::kable()
```

# Translate `dbplyr` into `SQL`

```{r}
flights_db %>%
  show_query() # Display equivalent SQL.

# Now, say we were interested in some kind of more complex manipulation.
delays <- flights_db %>% 
  group_by(carrier, origin) %>% 
  summarise(avg_dep_delay = mean(dep_delay),
            avg_arr_delay = mean(arr_delay))

# Take a look.
delays %>% 
  knitr::kable()

# In SQL.
delays %>% 
  show_query()

```

# How to vignette

