---
title: "twitter"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

I want to find some tweets where we discuss my visit to Stockholm. So, I wish to search my twitter feed for the character string `"Stockholm"`. 

I haven't tried twitter scraping before, this seems as good as anywhere to start. 

I searched for the terms "tidyverse", "twitter", "scrape" and found a [tutorial](https://idc9.github.io/stor390/notes/API/twitter/rtweet.html) about the `rtweet` package. Seems to be mentioned often enough and recently enough for it to be a good candidate. 

Alrighty, let's begin.

```{r Load packages}
library(tidyverse)
library(rtweet)
library(rvest) # Another possible package to investigate.

```

I'm not entirely sure what all this business of access tokens is for. I wonder if I need to set them just to scrape the public feed?

```{r try timeline}
# timeline <- get_timeline("cantabile") # This did not work.

```

## Getting access to twitter

For this part, I was directed to [these instructions](http://rtweet.info/articles/auth.html). I was curious to find out if I was required to set this up just to access my feed; i.e., not write to it. I found I did need to set this up. 

```{r create token}
# App
# appname <- "cantabilertweet"

# api key stored in object 'key'
# secret stored in object secret

# twitter_token <- create_token(app = appname,
#                               consumer_key = key,
#                               consumer_secret = secret)

```

## Scraping twitter

Okay, let's try this again.

```{r trying again}
cantabile_timeline <- get_timeline("cantabile", n = 3200)

# Take a look.
cantabile_timeline %>% str(max.level = 1)

```

## Find the string `"Stockholm"`

Let's make sure I understand how strings work. I may need to go to the `stringr` cheatsheet.

```{r Testing out strings}

stockholm_string <- "Stockholm is a very fine place."

# This doesn't work.
"Stockholm" %in% stockholm_string

# What about this?
"Stockholm" %in% str_split(stockholm_string, pattern = " ")

# Curious.
str_split(stockholm_string, pattern = " ")

# Is it because of its class?
str_split(stockholm_string, pattern = " ") %>% class()

# Make it a character vector.
stockholm_vector <- stockholm_string %>% str_split(pattern = " ")

# Class of vector
stockholm_vector %>% class()

# Take a look.
stockholm_vector

# Try converting to character string.
"Stockholm" %in% stockholm_vector[[1]]
```

## Extract my tweets that mention Stockholm

```{r Filter to my tweets}
# I hope my interpretation of the variables in the tibble is correct.

stockholm_tweets <- cantabile_timeline %>% 
  filter(is_quote == FALSE, # Remove quotes.
         is_retweet == FALSE, # Remove retweets.
         is.na(reply_to_status_id), # Remove replies.
         grepl("Stockholm", text) | grepl("stockholm", text)) # Only those that mention "Stockholm"

# Take a look.
stockholm_tweets$twit_vector[[1]]


# Testing that Stockholm produces what I want.
stockholm_tweets$stockholm %>% table()

# So, why does this work?
stockholm_tweets$text[[1]] %>% str_split(pattern = " ")

# But not when I map over text?

# Take a look.
stockholm_tweets %>% 
  select(created_at, text, status_id) %>% 
  knitr::kable()

```


## Extract responses to those tweets

```{r Try a join}
# Or could just use a filter.
tweets_replies <- cantabile_timeline %>% 
  mutate( 
    # See if tweet was a response to stockholm mentioning tweet.
    reply_stockholm = reply_to_status_id %in% stockholm_tweets$status_id
    ) %>%
  filter(
    # Get the replies.
    reply_stockholm == TRUE
  )

cantabile_timeline %>% 
  filter(reply_to_status_id == stockholm_tweets$status_id[[1]])


```



