---
title: "meta-analysis of medians"
subtile: "with `varameta`"
author: "Charles T. Gray"
date: "useR! 2018 Wednesday July 11"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, echo=FALSE, message=FALSE}
library(tidyverse)
library(varameta)
library(metafor)

```

## in a nutshell

meta-analysis is a statistical method of evidence synthesis of many studies

conventional tools for meta-analysis require an *effect* and a **variance** of that effect

why? $\because$ *inverse-variance weighting* of studies

### example from R 

[`metafor`](https://www.google.com/search?client=ubuntu&channel=fs&q=metafor%5D&ie=utf-8&oe=utf-8)::rma requires arguments $y_i$ and $v_i$

### but what if there is no variance reported?

what if the effect is reported as a median and the measure of spread is given as an interquartile range?

## in this talk

- a woefully glib intro to meta-analysis 
- an illustrative meta-analysis dataset 
- exploratory shiny apps
- current solutions
- `varameta` 

# meta-analysis 

## meta-analysis

- meta-analysis is a method of *evidence synthesis* 
- it is a way of combining together many studies' results
- frequently impractical to work with anything other than a few summary statistics for each study

## d-dimer levels in preeclampsia

```{r echo = FALSE}
varameta::pinheiro_data %>% 
  rename(c_c = control_centre, 
         s_c = control_spread,
         n_t = control_n,
         c_t = treatment_centre,
         s_t = treatment_spread,
         n_t = treatment_n,
         c = centre_type,
         s = spread_type) %>% 
  knitr::kable()

```

`c_c` := control centre, `t_c` := treatment centre, `n_c` := control n

## does the treatment work?

say we're interested in the effect of a medical treatment

```{}
this study's effect = true effect + some error 
```

### to maths it 

assume $K$ studies are randomly drawn from a larger population, and that the $k^{th}$ effect can thought of as 

$$
y_k = \mu + \varepsilon_k
$$

with $\mu$ the true population effect $\varepsilon \sim N(0, \sigma^2)$ representing sampling error

## inverse-variance weighting 

the model estimates the **weighted** average of true effects 

$$
\theta_w = \frac{\sum w_i \theta_i}{\sum w_i}
$$

using *inverse variance* $w_i = 1/v_i$

**this is why asymmetric spread measures pose a challenge in meta-analysis**

## not all studies are created equal

weighting is **one** way to account for the strength or weakness of a study

but what about differences 

### studies are *not* the same 

say, what if a study was conducted at a university and the participants were all aged < 25? 

what if the drug was more effective on young people? 

## meta-analysis: random effects  

```{}
this study's effect = true effect + study's unique factors + some error 
```

the effect of the $k^{\text{th}}$ study is assumed to be

$$
y_k = \mu + \theta_k + \varepsilon_k
$$

where $\theta_k \sim N(0, \tau^2)$ is the random effect estimating variation between 
studies and $\varepsilon \sim N(0, \sigma^2)$
is a random effect estimating the sampling error

we can also add moderators as we do with linear models to control for various conditions 

## returning to our example

```{r echo = TRUE}
varameta::pinheiro_data %>% select(study, year, centre_type, spread_type) %>% knitr::kable()
```


## existing methods

leave the medians out 
```{r fig.align='center'}
ma_means_only <- pinheiro_data %>%
  # choose on the studies reporting means
  filter(centre_type == "mean") %>% 
   # calculate mean difference
  mutate(md = control_centre - treatment_centre,
         # variance of mean difference
         md_var = control_spread^2 + treatment_spread^2 
         ) %>%   
  rma(yi = md, vi = md_var, data = ., slab = study, measure = "MD") 
# arguments required: effect and the variance of the effect 
```

## means only

a *forest* plot of the means-only meta-analysis

```{r}
ma_means_only %>% forest()
```

## convert the medians

several methods have been developed to approximate the mean and the standard deviation from reported quantiles


## an estimation of the approximation

we can estimate an approximation of the variance of the sample median

$$
Var(M) \approx \frac 1 {4n[f(\nu)]^2} \dot\approx \frac  1 {4 n [g(M)]^2}
$$

we can also use this to approximate the difference of medians and the log-ratio of medians

### but what choice of $g$?

```{}
shiny::runApp("mikrokosmos/shinyv", launch.browser = TRUE)
```

## simulations

```{}
shiny::runApp("mikrokosmos/shinyci", launch.browser = TRUE)
```

## now we can meta-analyse medians

```{r}
ma_medians_only <- pinheiro_data %>%
  # choose only studies reporting medians
  filter(centre_type == "median") %>% 
  mutate(control_var = pmap_dbl( # calculate control variance
    list(centre = control_centre,
         spread = control_spread,
         n = control_n,
         centre_type = centre_type,
         spread_type = spread_type), varameta::effect_se),
    treatment_var = pmap_dbl( # calculate treatment variance
    list(centre = treatment_centre,
         spread = treatment_spread,
         n = treatment_n,
         centre_type = centre_type,
         spread_type = spread_type), varameta::effect_se),
    md = control_centre - treatment_centre, # median difference
    md_var = control_var^2 + treatment_var^2) %>% 
  rma(yi = md, vi = md_var, data = ., slab = study)

```

***

```{r}
ma_medians_only %>% forest()
```


## compare means and medians

```{r echo = FALSE}
ma_means_n_medians <- pinheiro_data %>%
  # choose only studies reporting medians
  mutate(control_var = pmap_dbl( # calculate control variance
    list(centre = control_centre,
         spread = control_spread,
         n = control_n,
         centre_type = centre_type,
         spread_type = spread_type), varameta::effect_se),
    treatment_var = pmap_dbl( # calculate treatment variance
    list(centre = treatment_centre,
         spread = treatment_spread,
         n = treatment_n,
         centre_type = centre_type,
         spread_type = spread_type), varameta::effect_se),
    md = control_centre - treatment_centre, # median difference
    md_var = control_var^2 + treatment_var^2) %>% 
  rma(yi = md, vi = md_var, data = ., slab = study, mod = (centre_type == "mean"))

ma_means_n_medians %>% forest()

```


## next steps

- tidy up the package and get it out there
- add all the simulations
- write up the paper
- shiny website dashboard for non-R users

### extensions

- the `metameta` pkg that *tidies* meta-analyses
- what can we infer about *distributions* from limited information? (lambda-distribution exploration)  
