---
title: "meta-analysis of medians"
subtile: "with `varameta`"
author: "Charles T. Gray"
date: "useR! 2018 Wednesday July 11"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, echo=FALSE, message=FALSE}
library(tidyverse)
library(varameta)

```

## in a nutshell

meta-analysis is a statistical method of evidence synthesis of many studies

conventional tools for meta-analysis require an *effect* and a **variance** of that effect

why? $\because$ *inverse-variance weighting* of studies

### example from R 

[`metafor`](https://www.google.com/search?client=ubuntu&channel=fs&q=metafor%5D&ie=utf-8&oe=utf-8)::rma requires arguments $y_i$ and $v_i$

### but what if there is no variance reported?

what if the effect is reported as a median and the measure of spread is given as an interquartile range?

## in this talk

- a woefully glib intro to meta-analysis 
- an illustrative meta-analysis dataset 
- exploratory shiny apps
- current solutions
- `varameta` 

# meta-analysis 

## meta-analysis

- meta-analysis is a method of *evidence synthesis* 
- it is a way of combining together many studies' results
- frequently impractical to work with anything other than a few summary statistics for each study

## d-dimer levels in preeclampsia

```{r echo = FALSE}
varameta::pinheiro_data %>% 
  rename(c_c = control_centre, 
         s_c = control_spread,
         n_t = control_n,
         c_t = treatment_centre,
         s_t = treatment_spread,
         n_t = treatment_n,
         c = centre_type,
         s = spread_type) %>% 
  knitr::kable()

```
$$\varepsilon \sim N(0, \sigma^2)$$

`c_c` := control centre, `t_c` := treatment centre, `n_c` := control n
 to 
## does it work?

say we're interested in the effect of a medical treatment

```{}
this study's effect = true effect + some error 
```

### to maths it 

assume $K$ studies are randomly drawn from a larger population, and that the $k^{th}$ effect can thought of as 

$$
y_k = \mu + \varepsilon_k
$$

with $\mu$ the true population effect $\varepsilon \sim N(0, \sigma^2)$ representing sampling error

## not all studies are created equal

say, what if a study was conducted at a university and the participants were all aged < 25? 



## meta-analysis: random effects  

```{}
this study's effect = true effect + study's unique factors + some error 
```

For the $k^{\text{th}}$

$$
y_k = \mu + \theta_k + \varepsilon_k
$$

where $\theta_k \sim N(0, \tau^2)$ is the random effect estimating variation between 
studies and $\varepsilon \sim N(0, \sigma^2)$
is a random effect estimating the sampling error

## current solutions

## a more scientifically cromulent estimator

```{}
shiny::runApp("mikrokosmos/shinyv", launch.browser = TRUE)
```

## simulations

```{}
shiny::runApp("mikrokosmos/shinyci", launch.browser = TRUE)
```

